---
title: "world-cafe study (informing scenario texts)"
author: "Julius Fenn, Louisa Estadieu"
format:
  html:
    toc: true
    toc-depth: 3
    html-math-method: katex
---

```{r}
#| echo: false
#| warning: false

# sets the directory of location of this script as the current directory
# setwd(dirname(rstudioapi::getSourceEditorContext()$path))

########################################
# load packages
########################################
require(pacman)
p_load('tidyverse', 'jsonlite', 'magrittr', 'xlsx',
       'stargazer', 'psych', 'jtools', 'DT', 'ggstatsplot', 
       'lavaan', 
       'regsem', 'MplusAutomation')

########################################
# load data
########################################
##### JATOS file
setwd("data")
# dir()
suppressMessages(read_file('jatos_results_data_20231208084224.txt') %>%
  # ... split it into lines ...
  str_split('\n') %>% first() %>%
  # ... filter empty rows ...
  discard(function(x) x == '') %>%
  # ... parse JSON into a data.frame
  map_dfr(fromJSON, flatten=TRUE)) -> dat
setwd("..")

########################################
# load functions
########################################
setwd("../functions")
for(i in 1:length(dir())){
  # print(dir()[i])
  source(dir()[i], encoding = "utf-8")
}
rm(i)
```

# Notes

Remark: ...

# prepare data

## set up data.frame

```{r}
########################################
# create counter variable for data set
########################################
dat$ID <- NA

tmp_IDcounter <- 0
for(i in 1:nrow(dat)){
  if(!is.na(dat$sender[i]) && dat$sender[i] == "Greetings"){
    # tmp <- dat$prolific_pid[i]
    tmp_IDcounter = tmp_IDcounter + 1
  }
  dat$ID[i] <- tmp_IDcounter
}


########################################
# keep only complete data sets
########################################
sum(table(dat$ID) != max(table(dat$ID)))
sum(table(dat$ID) == max(table(dat$ID)))
dat <- dat[dat$ID %in% names(table(dat$ID))[table(dat$ID) == max(table(dat$ID))],]

########################################
# json (from JATOS) to 2D data.frame
########################################
tmp_notNumeric <- str_subset(string = colnames(dat), pattern = "^meta")
tmp_notNumeric <- str_subset(string = tmp_notNumeric, pattern = "labjs|location", negate = TRUE)

# tmp_numeric <- str_subset(string = colnames(dat), pattern = "^affImgAffect|^CRKQ|^CCSQ|^CMQ|^GCB")


vec_ques <- c("dummy_informedconsent",
              tmp_notNumeric,
              
              "applicationsSR", "applicationsSRdefinition",
              
              "benefitsSR", "benefitsSRdefinition",
              "risksSR", "risksSRdefinition",
              
              "socialBenefitsSR", "socialBenefitsSRdefinition", 
              "socialRisksSR", "socialRisksSRdefinition",
              
              "sustainableSR", "sustainableSRdefinition",
              
              "feedback_critic")

vec_notNumeric = c("dummy_informedconsent",
              tmp_notNumeric,
              
              "applicationsSR", "applicationsSRdefinition",
              
              "benefitsSR", "benefitsSRdefinition",
              "risksSR", "risksSRdefinition",
              
              "socialBenefitsSR", "socialBenefitsSRdefinition", 
              "socialRisksSR", "socialRisksSRdefinition",
              
              "sustainableSR", "sustainableSRdefinition",
              
              "feedback_critic")

questionnaire <- questionnairetype(dataset = dat, 
                                        listvars = vec_ques, 
                                        notNumeric = vec_notNumeric)
```


## get reaction times for single components

*not needed*

## clean data (if needed)

*not needed*

# describe data 

## sample description

```{r}
## number of participants
nrow(questionnaire)
```

# open questions

## applications of soft robots

**open question:**  What are the most promising applications of soft robots over their rigid counterparts within your field of expertise?

```{r}
DT::datatable(questionnaire[, c("applicationsSR","applicationsSRdefinition")], options = list(pageLength = 5)) 
```

## main benefits and risks of soft robots

**open questions:** 

* In your expert opinion, what are the main benefits of soft robots compared to rigid robots?
* In your expert opinion, what are the main risks of soft robots compared to rigid robots?

```{r}
DT::datatable(questionnaire[, c("benefitsSR","benefitsSRdefinition",
                                "risksSR","risksSRdefinition")], options = list(pageLength = 5)) 
```

## social benefits and risks of soft robots

**open questions:** 

*  From your expert perspective, what do you identify as the primary social benefits of soft robots compared to rigid robots? 
*  From your expert perspective, what do you identify as the primary social risks of soft robots compared to rigid robots?

```{r}
DT::datatable(questionnaire[, c("socialBenefitsSR","socialBenefitsSRdefinition",
                                "socialRisksSR","socialRisksSRdefinition")], options = list(pageLength = 5)) 
```


## environmental impacts of soft robots

**open question:**  From your expert point of view, could you elaborate on the potential environmental impacts of soft robots, considering aspects like energy efficiency, and end-of-life disposal, particularly in comparison to rigid robots?

```{r}
DT::datatable(questionnaire[, c("sustainableSR","sustainableSRdefinition")], options = list(pageLength = 5)) 
```


### save as Excel

as .xlsx file

```{r}
tmp_dat <- questionnaire[, c("ID",
"applicationsSR","applicationsSRdefinition",
"benefitsSR","benefitsSRdefinition",
"risksSR","risksSRdefinition",
"socialBenefitsSR","socialBenefitsSRdefinition",
"socialRisksSR","socialRisksSRdefinition",
"sustainableSR","sustainableSRdefinition",
"feedback_critic")]
xlsx::write.xlsx2(x = tmp_dat, file = "outputs/openQuestions.xlsx")
```


## general feedback, critic

```{r}
tmp_dat <- questionnaire[questionnaire$feedback_critic != "" & !is.na(questionnaire$feedback_critic), c("ID","feedback_critic")]
DT::datatable(tmp_dat, options = list(pageLength = 5)) 
```
